---
title: "OBIWAN BEHAVIORAL ANALYSIS"
author: "David Munoz Tord"
date: '2020-12-03'
output:
  pdf_document:
    dev: cairo_pdf
  html_document: default
repro:
  data:
    HED: data/HEDONIC.csv
    INST: data/INST.csv
    PAV: data/PAV.csv
    PIT: data/PIT.csv
    info: data/info.csv
    intern: data/internal.csv
  packages:
  - aaronpeikert/repro@adb5fa569
  - crsh/papaja@devel
  - tinylabels
  - apaTables
  - MBESS
  - afex
  - car
  - ggplot2
  - plyr
  - dplyr
  - tidyr
  - reshape
  - Hmisc
  - Rmisc
  - ggpubr
  - ez
  - gridExtra
  - plotrix
  - parallel
  - emmeans
  - BayesFactor
  - effectsize
  - devtools
  - misty
  - bayestestR
  - lspline
  - kableExtra
  - sjPlot
  - knitr
  - XML
  - rlist
  - janitor
  - optimx
  scripts: R/clean.R
  apt:
    - octave
    - gnuplot
    - libgsl0-dev
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warnings=FALSE)

library(repro)
# load packages from yaml header
automate_load_packages()
# include external scripts
automate_load_scripts()
# load data
info <- automate_load_data(info, read.csv, stringsAsFactors = T)
intern <- automate_load_data(intern, read.csv, stringsAsFactors = T)
PAV <- automate_load_data(PAV, read.csv, stringsAsFactors = T)
INST <- automate_load_data(INST, read.csv, stringsAsFactors = T)
PIT <- automate_load_data(PIT, read.csv, stringsAsFactors = T)
HED <- automate_load_data(HED, read.csv, stringsAsFactors = T)
```

## Setup

May I suggest running `repro::automate()`? This will create a `Dockerfile` & `Makefile` based on every RMarkdown in this folder and the special yamls in them.
add ENV DEBIAN_FRONTEND=noninteractive
If you are unsure weather or not you have `git` `make` & `docker`.

```{r check, eval=TRUE}
check_git()
check_make()
check_docker()
```

```{r options, echo=FALSE, include=FALSE}
options(scipen = 666, warn=-1, contrasts=c("contr.sum","contr.poly"), mc.cores = parallel::detectCores()) #remove scientific notation # remove warnings #set contrasts to sum !
set.seed(666) #set random seed
control = lmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')) #set "better" lmer optimizer #nolimit # yoloptimizer
emm_options(pbkrtest.limit = 5000) #increase repetitions limit
cl <- parallel::detectCores() #to mulithread
source('R/plots.R', echo=F)# plot specification
source('R/utils.R', echo=F)# useful functions
```

```{r clean, echo=FALSE, include=FALSE}
# this chunk runs R/clean.R (listed in the YAML)
```

## Demographics
### Summary statistics:
```{r demographgics}
df = PAV.means; df$intervention = as.factor(revalue(as.factor(df$intervention), c("0"="Placebo", "1"="Liraglutide")));#using pav.means but oculd be any other

AGE = ddply(df,~intervention,summarise,mean=mean(age),sd=sd(age), min = min(age), max = max(age));
AGE %>%
  kbl(caption ="AGE", digits = 2) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

BMI = ddply(df,~intervention,summarise,mean=mean(BMI1),sd=sd(BMI1), min = min(BMI1), max = max(BMI1)); 
BMI %>%
  kbl(caption ="BMI", digits = 2) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

GENDER = ddply(df, .(id, intervention), summarise, gender=mean(as.numeric(gender)))  %>%
  group_by(gender, intervention) %>%
  tally(); GENDER$gender = as.factor(revalue(as.factor(GENDER$gender), c("1"="Men", "2"="Women"))); 
  GENDER %>% kbl(caption ="GENDER") %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

N_group = ddply(df, .(id, intervention), summarise, group=mean(as.numeric(intervention)))  %>%
  group_by(intervention) %>% tally();
N_group %>%
  kbl(caption ="Group") %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')
```
# Description

# Pavlvovian Conditioning Task (Analysis: Latency)
Formula = Latency ~ condition*intervention + age + gender + thirsty + hungry + BMI_t1 +  diff_base_RT + Error(id/condition)\
Latency = time to detect the target (ms)    &     condition = CS+ or CS- \
diff_base = baseline latency differences (mean(CS-) -  mean(CS+)) 
```{r PAV_RT, echo=FALSE, include=FALSE, cache=TRUE}
# -------------------------------------- RT
model = aov_car(RT ~ condition*intervention + age + gender + thirsty + hungry + BMI_t1 +  diff_base + Error(id/condition), PAV.means, factorize = F, anova_table = list(correction = "GG", es = "none"))
table = nice(model); 

#calculate Partial eta-squared and its 90 % CI for each effect
pes_CI = pes_ci(RT ~ condition*intervention + age + gender + thirsty + hungry + BMI_t1 +  diff_base + Error(id/condition), PAV.means); 
table$`PES` = pes_CI[,1]
table$`Lower CI` = pes_CI[,2]
table$`Upper CI` = pes_CI[,3]

#calculate exclusion BF01 for each effect
test = extractBF(generalTestBF(RT ~ condition*intervention + condition*age + condition*gender + condition*thirsty + condition*hungry + condition*BMI_t1 + condition*diff_base + id, data= PAV.means, whichRandom = 'id', neverExclude =  'id', whichModels ="top")); BF = 1/test[1] #switch to BF10 inclusion)); BF = 1/test[1] #switch to BF10 inclusion
table$BF10 = BF$bf[order(c(15,14,13,13,11,10,9,7,6,5,4,3,2,1,8))] # reorder

mod <- lm(RT ~ condition*intervention + condition*age + condition*gender + condition*thirsty + condition*hungry + condition*BMI_t1 + condition*diff_base, data = PAV.means)

ref_grid(mod)  #triple check everything is centered at 0
tab_model(mod, show.p = F,show.intercept = F, show.se = T, title ="", show.re.var = F, digits = 3, dv.labels = "Latency", emph.p = TRUE, file = "tmp/temp1.html")#pred.labels=c("CS+", "Lean", "Interaction (Lean:CS+)")
```
\
```{r PAV_RT_mod}
tables <- list.clean(readHTMLTable("tmp/temp1.html"), fun = is.null, recursive = FALSE)
tables2 = tables[[1]] %>% janitor::row_to_names(row_number = 1)
tables2 <- as.matrix(tables2) %>% as_tibble()
tables2[is.na(tables2)] <- ""
tables2[1:15,1:4] %>% kbl(caption ="Latency (ms)" ) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
tmp =tables2[16:17,1:2]
names(tmp) <- NULL
tmp %>% kbl() %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) 
```
\
```{r PAV_RT_res}
table %>% kbl(digits = 2) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
```
\
```{r PAV_RT_cont, echo=FALSE, include=FALSE, cache=TRUE}
#Estimated contrast mean and 95% CI\ (one sided test  side = "<")
#p_cond = emmeans(mod, pairwise~ condition, side = "<"); p_cond #for condition (CS+ < CS- left sided!)
#CI_cond = confint(emmeans(mod, pairwise~ condition),level = 0.95, method = c("boot"), nsim = 5000); 
#tab =as_tibble(CI_cond$contrasts); tab$contrast = "CS+ > CS-"

#tab %>% kbl() %>%
  #kable_styling(latex_options = "striped", position = "left", full_width = F) 
```
## Latency by condition
```{r PAV_RT_plot, echo=FALSE, warning=FALSE, cache=TRUE}
# RT
dfR <- summarySEwithin(df,
                       measurevar = "RT",
                       withinvars = "condition", 
                       idvar = "id")

dfR$cond <- ifelse(dfR$condition == "1", -0.25, 0.25)
PAV.means$cond <- ifelse(PAV.means$condition == "1", -0.25, 0.25)
PAV.means <- PAV.means %>% mutate(condjit = jitter(as.numeric(cond), 0.3),
                                  grouping = interaction(id, cond))

pp <- ggplot(PAV.means, aes(x = cond, y = RT, 
                            fill = condition, color = condition)) +
  geom_line(aes(x = condjit, group = id, y = RT), alpha = .3, size = 0.5, color = 'gray') +
  geom_flat_violin(scale = "count", trim = FALSE, alpha = .2, aes(fill = condition, color = NA))+
  geom_point(aes(x = condjit, shape = intervention), alpha = .3,) +
  geom_crossbar(data = dfR, aes(y = RT, ymin=RT-se, ymax=RT+se), width = 0.2 , alpha = 0.1)+
  ylab('Latency (ms)')+
  xlab('Conditioned stimulus')+
  scale_y_continuous(expand = c(0, 0), breaks = c(seq.int(200,800, by = 200)), limits = c(180,875)) +
  scale_x_continuous(labels=c("CS+", "CS-"),breaks = c(-.25,.25), limits = c(-.5,.5)) +
  scale_fill_manual(values=c("1"= pal[2], "-1"=  pal[1]), guide = 'none') +
  scale_color_manual(values=c("1"= pal[2], "-1"=  pal[1]), guide = 'none') +
  scale_shape_manual(name="Intervention", labels=c("Placebo", "Liraglutide"), values = c(1, 2)) +
  theme_bw()

plt = pp + averaged_theme 
pp + html_theme 
```
```{r PAV_RT_saveFIG, include=FALSE}
cairo_pdf('figures/Figure_PavlovianRT_Lira.pdf')
print(plt)
dev.off()
```
## Analysis: Pleasantness Ratings (Pavlovian Cue)

Formula = Pleasantness ratings ~ condition*intervention + age + gender + thirsty + hungry + BMI_t1 +  diff_base_lik + Error(id/condition)\
Ratings = how pleasant is the clue (0-100, no repetitions)   &   condition = CS+ or CS-
diff_base_lik = baseline liking differences (mean(CS+) -  mean(CS-)) 
```{r PAV_Lik_mod, cache=TRUE, include=FALSE, message=FALSE}
# -------------------------------------- Liking
model = aov_car(liking ~ condition*intervention + age + gender + thirsty + hungry + BMI_t1 +  diff_base_lik + Error(id/condition), data= df, factorize = F, anova_table = list(correction = "GG", es = "none"))
table = nice(model); 

#calculate Partial eta-squared and its 90 % CI for each effect
pes_CI = pes_ci(liking ~ condition*intervention + age + gender + thirsty + hungry + BMI_t1 +  diff_base_lik + Error(id/condition), PAV.means); 
table$`PES` = pes_CI[,1]
table$`Lower CI` = pes_CI[,2]
table$`Upper CI` = pes_CI[,3]

#calculate exclusion BF01 for each effect
test = extractBF(generalTestBF(liking ~ condition*intervention + condition*age + condition*gender + condition*thirsty + condition*hungry + condition*BMI_t1 + condition*diff_base_lik + id, data= PAV.means, whichRandom = 'id', neverExclude =  'id', whichModels ="top")); BF = 1/test[1] #switch to BF10 inclusion)); BF = 1/test[1] #switch to BF10 inclusion
table$BF10 = BF$bf[order(c(15,14,13,13,11,10,9,7,6,5,4,3,2,1,8))] # reorder
table$BF10[6] = formatC(BF$bf[11], format = "e", digits = 2)

mod <- lm(liking ~  condition*intervention + condition*age + condition*gender + condition*thirsty + condition*hungry + condition*BMI_t1 + condition*diff_base_lik, data = PAV.means) # for estimated means

ref_grid(model)  #triple check everything is centered at 0
tab_model(mod, show.p = F,show.intercept = F, show.se = T,  title ="", show.re.var = F, digits = 3, dv.labels = "Pleasantness Ratings (Pavlovian Cue)", emph.p = TRUE, file = "tmp/temp2.html")#pred.labels=c("CS+", "Lean", "Interaction (Lean:CS+)")
```
```{r PAV_lik_res}
tables <- list.clean(readHTMLTable("tmp/temp2.html"), fun = is.null, recursive = FALSE)
tables2 = tables[[1]] %>% janitor::row_to_names(row_number = 1)
tables2 <- as.matrix(tables2) %>% as_tibble()
tables2[is.na(tables2)] <- ""
tables2[1:11,1:4] %>% kbl(caption ="Pleasantness Ratings (Pavlovian Cue)" ) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
tmp =tables2[12:13,1:2]
names(tmp) <- NULL
tmp %>% kbl() %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) 

table %>% kbl( digits = 2) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
```

## Pleasantness Ratings by condition (Pavlvovian Cue)
```{r PAV_LIK_plot, echo=FALSE, warning=FALSE, cache=TRUE}
dfL <- summarySEwithin(PAV.means,
                       measurevar = "liking",
                       withinvars = "condition", 
                       idvar = "id")

dfL$cond <- ifelse(dfL$condition == "1", -0.25, 0.25)

# Liking
pp <- ggplot(PAV.means, aes(x = cond, y = liking, 
                            fill = condition, color = condition)) +
  geom_line(aes(x = condjit, group = id, y = liking), alpha = .3, size = 0.5, color = 'gray' ) +
  geom_flat_violin(scale = "count", trim = FALSE, alpha = .2, aes(fill = condition, color = NA)) +
  geom_point(aes(x = condjit, shape = intervention), alpha = .3) +
  geom_crossbar(data = dfL, aes(y = liking, ymin=liking-se, ymax=liking+se), width = 0.2 , alpha = 0.1)+
  ylab('Liking Ratings')+
  xlab('Conditioned stimulus')+
  scale_y_continuous(expand = c(0, 0), breaks = c(seq.int(0,100, by = 25)), limits = c(-0.05,100.5)) +
  scale_x_continuous(labels=c("CS+", "CS-"),breaks = c(-.25,.25), limits = c(-.5,.5)) +
  scale_fill_manual(values=c("1"= pal[2], "-1"=  pal[1]), guide = 'none') +
  scale_color_manual(values=c("1"= pal[2], "-1"=  pal[1]), guide = 'none') +
  scale_shape_manual(name="Intervention", labels=c("Placebo", "Liraglutide"), values = c(1, 2)) +
  theme_bw()


pp + html_theme 
plt = pp + averaged_theme 
```
```{r PAV_lik_saveFIG, include=FALSE}
cairo_pdf('figures/Figure_PavlovianLiking_Lira.pdf')
print(plt)
dev.off()
```

# Instrumental Conditioning Task (Analysis)
Formula = Number of grips ~ spline*intervention + age + gender + thirsty + hungry + BMI_t1  + diff_base + Error(id/spline)\
grips = number of times participant exceeded the force threshold to acquire the reward (Milkshake)

```{r INST, cache=TRUE,  include=FALSE, message=FALSE}
model = aov_car(grips ~ spline*intervention + age + gender + thirsty + hungry + BMI_t1  + diff_base + Error(id/spline), data= INST.means, factorize = F, anova_table = list(correction = "GG", es = "none"))
table = nice(model); 

#calculate Partial eta-squared and its 90 % CI for each effect
pes_CI = pes_ci(grips ~ spline*intervention + age + gender + thirsty + hungry + BMI_t1  + diff_base + Error(id/spline), INST.means); 
table$`PES` = pes_CI[,1]
table$`Lower CI` = pes_CI[,2]
table$`Upper CI` = pes_CI[,3]

#calculate exclusion BF01 for each effect
test = extractBF(generalTestBF(grips ~ spline*intervention + spline*age + spline*gender + spline*thirsty + spline*hungry + spline*BMI_t1  + spline*diff_base + id, data= INST.means, whichRandom = 'id', neverExclude =  'id', whichModels ="top")); BF = 1/test[1] #switch to BF10 inclusion)); BF = 1/test[1] #switch to BF10 inclusion
table$BF10 = BF$bf[order(c(15,14,13,13,11,10,9,7,6,5,4,3,2,1,8))] # reorder
#table$BF10[6] = formatC(BF$bf[11], format = "e", digits = 2)

mod <- lm(grips ~ spline*intervention + spline*age + spline*gender + spline*thirsty + spline*hungry + spline*BMI_t1  + spline*diff_base, data = INST.means) # for estimated means


#model$Effect = c('trial-spline(5)', 'group', 'age', 'gender', 'thirsty', 'hungry', 'trial-spline(5)*group') #make it nice

tab_model(mod, show.p = F,show.intercept = F, show.se = T, title ="", show.re.var = F, digits = 3, dv.labels = "Number of grips", emph.p = TRUE, file = "tmp/temp3.html") # pred.labels=c("trial &#60 5", "trial > 5", "group[1]", "age", "gender[1]", "thirsty", "hungry", "trial &#60 5 * group[1]", "trial > 5 * group[1]")
```
```{r INST_mod_tab}
tables <- list.clean(readHTMLTable("tmp/temp3.html"), fun = is.null, recursive = FALSE)
tables2 = tables[[1]] %>% janitor::row_to_names(row_number = 1)
tables2 <- as.matrix(tables2) %>% as_tibble()
tables2[is.na(tables2)] <- ""
tables2[1:15,1:4] %>% kbl(caption ="Number of grips", digits = 2) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F)  %>%  row_spec(0,bold=T,align='c')

tmp =tables2[16:17,1:2]
names(tmp) <- NULL
tmp %>% kbl() %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) 
```
```{r INST_res}
table %>% kbl(caption ="") %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
```

## Number of Grips by learning phasis
```{r INST_plot, echo=FALSE, warning=FALSE, cache=TRUE}
dfL <- summarySEwithin(INST.means,
                       measurevar = "grips",
                       withinvars = "spline", 
                       idvar = "id")

dfL$cond <- ifelse(dfL$spline == "1", -0.25, 0.25)
INST.means$cond <- ifelse(INST.means$spline == "1", -0.25, 0.25)
INST.means <- INST.means %>% mutate(condjit = jitter(as.numeric(cond), 0.3),grouping = interaction(id, cond))


# grips
pp <- ggplot(INST.means, aes(x = cond, y = grips, 
                            fill = spline, color = spline)) +
  geom_line(aes(x = condjit, group = id, y = grips), alpha = .3, size = 0.5, color = 'gray' ) +
  geom_flat_violin(scale = "count", trim = FALSE, alpha = .2, aes(fill = spline, color = NA)) +
  geom_point(aes(x = condjit, shape = intervention), alpha = .3) +
  geom_crossbar(data = dfL, aes(y = grips, ymin=grips-se, ymax=grips+se), width = 0.2 , alpha = 0.1)+
  ylab('Number of grips')+
  xlab('Learning phasis')+
  scale_y_continuous(expand = c(0, 0), breaks = c(seq.int(0,30, by = 5)), limits = c(-0.05,30.5)) +
  scale_x_continuous(labels=c("Early", "Late"),breaks = c(-.25,.25), limits = c(-.5,.5)) +
  scale_fill_manual(values=c("1"= pal[4], "0"=  pal[1]), guide = 'none') +
  scale_color_manual(values=c("1"= pal[4], "0"=  pal[1]), guide = 'none') +
  scale_shape_manual(name="Intervention", labels=c("Placebo", "Liraglutide"), values = c(1, 2)) +
  theme_bw()


pp + html_theme 
plt = pp + averaged_theme 
```
```{r INST_saveFIG, echo=FALSE, include = FALSE, warning=FALSE}
cairo_pdf('figures/Figure_Instrumental_trial.pdf')
print(plt)
dev.off()
```
```{r INST_plot2, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
## Number of Grips over time
# dfTRIAL <- summarySEwithin(INST2, na.rm=TRUE,
#                            measurevar = "grips",
#                            withinvars = "trial",
#                            idvar = "id")
# 
# 
# dfTRIAL$trial       <- as.numeric(dfTRIAL$trial)
# 
# dfTRIALg <- summarySEwithin(INST2, na.rm=TRUE,
#                            measurevar = "grips",
#                            withinvars = "trial",
#                            betweenvars = "intervention",
#                            idvar = "id")
# 
# dfTRIALg$trial       <- as.numeric(dfTRIALg$trial)
# 
# dfTRIAL$x = dfTRIAL$trial; dfTRIAL$y = dfTRIAL$grips
# splinelm <- lm(y ~ lspline(x, 5), data=dfTRIAL)
# 
# 
# pp <- ggplot(dfTRIAL, aes(x =trial, y = grips)) +
#   geom_point(data = dfTRIALg, aes(shape = intervention), alpha = 0.3, color = 'black') +
#   geom_point(data = dfTRIAL, alpha = 0.5, color = pal[4], shape = 18) +
#   #geom_line(color = pal[4]) +
#   geom_smooth(method="lm", formula=formula(splinelm), color="tomato",fill = pal[4], size=0.7) + #addd this for lsplines
#   #geom_ribbon(aes(ymin=grips-se, ymax=grips+se), fill = pal[4], alpha = 0.3)+
#   ylab('Number of Grips')+
#   xlab('Trial') +
#   scale_y_continuous(expand = c(0, 0),  limits = c(10.5,15.05),  breaks=c(seq.int(11,15, by = 1))) +
#   scale_x_continuous(expand = c(0, 0),  limits = c(0,15.1),  breaks=c(seq.int(1,15, by = 1))) +
#   scale_shape_manual(name="Intervention", labels=c("Placebo", "Liraglutide"), values = c(1, 2, 18)) +
#   theme_bw()
# 
# pp + html_theme + theme(legend.position=c(.9,.88), axis.text.x = element_text(size = 16))
# plt = pp + averaged_theme + theme(legend.position=c(.9,.88), axis.text.x = element_text(size = 16))
```


# Pavlvovian-Instrumental Transfer (PIT) Task (Analysis)
Formula = Mobilized effort ~ condition*group + age + gender+ thirsty + hungry + (condition|id)\
Mobilized effort = Area under the curve of the force exerted exceeding the delivery threshold during Pavlvoian cue presentation
```{r PIT, echo=FALSE, include=FALSE, cache=TRUE}
# -------------------------------------- STATS -----------------------------------------------
### Linear Mixed Models 
# Mixed is just a wrapper for lmer to get p-values from parametric bootstrapping #but set to method "LRT" and remove "args_test" to quick check ##
#model = mixed(formula, data = PIT.clean, method = "LRT", control = control, REML = FALSE)
#model = mixed(formula, data = PIT.clean, method = "PB", control = control, REML = FALSE, args_test = list(nsim = 10000, cl=cl)) 

model = aov_car(AUC ~ condition*group + age + gender+ thirsty + hungry +  Error(id/condition), data= PIT.means, factorize = F, anova_table = list(correction = "GG", es = "none"))
table = nice(model); 

#calculate Partial eta-squared and its 90 % CI for each effect
pes_CI = pes_ci(AUC ~ condition*group + age + gender+ thirsty + hungry +  Error(id/condition), PIT.means); 
table$`PES` = pes_CI[,1]
table$`Lower CI` = pes_CI[,2]
table$`Upper CI` = pes_CI[,3]

#calculate exclusion BF01 for each effect
test = extractBF(generalTestBF(AUC ~ condition*group + condition*age + condition*gender + condition*thirsty + condition*hungry + id, data= PIT.means, whichRandom = 'id', neverExclude =  'id', whichModels ="top")); BF = 1/test[1] #switch to BF10 inclusion)); BF = 1/test[1] #switch to BF10 inclusion
table$BF10 = BF$bf[order(c(11,10,9,8,7,5,4,3,2,1,6))] # reorder

mod <- lmer(AUC ~ condition*group + condition*age + condition*gender+ condition*thirsty + condition*hungry + (condition|id), data = PIT.clean, control = control, REML = T) # recompute model with REML = T now for further analysis

tab_model(mod, show.p = F,show.intercept = F, show.se = T, title ="", show.re.var = F, digits = 3, dv.labels = "Mobilized effort (a.u.)", file = "tmp/temp4.html") #, pred.labels=c("CS+", "Lean", "Interaction (Lean:CS+)")
```
\
```{r PIT_mod, echo=FALSE}
tables <- list.clean(readHTMLTable("tmp/temp4.html"), fun = is.null, recursive = FALSE)
tables2 = tables[[1]] %>% janitor::row_to_names(row_number = 1)
tables2 <- as.matrix(tables2) %>% as_tibble()
tables2[is.na(tables2)] <- ""
tables2[1:11,1:4] %>% kbl(caption ="Mobilized effort (a.u.)" ) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F)  %>%  row_spec(0,bold=T,align='c')

tmp =tables2[12:15,1:2]
names(tmp) <- NULL
tmp %>% kbl() %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F)  

```

```{r PIT_res}
table %>% kbl( digits = 2) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
```
\
```{r PIT_cont, echo=FALSE, include=FALSE, cache=TRUE}
#p_cond = emmeans(mod, pairwise~ condition, side = ">"); p_cond #for condition (CS+ > CS- right sided)
#CI_cond = confint(emmeans(mod, pairwise~ condition),level = 0.95, method = c("boot"), nsim = 5000); #CI_cond$contrasts #get CI condition

inter = emmeans(model, pairwise~ condition|group, adjust = "tukey", side = ">")  #for group X condition (adjusted but still right sided)
CI_inter = confint(emmeans(model, pairwise~ condition|group),level = 0.95,method = c("boot"),nsim = 5000) ##get CI inter
tmp = as_tibble(inter$contrasts); 
tab =as_tibble(CI_inter$contrasts); tab$contrast = "CS+ > CS-"; tab$group = c("Lean", "Obese"); tab$T = tmp$t.ratio; tab$p.value = tmp$p.value; 
```
\
```{r PIT_cont_tab}
tab %>% kbl(caption = "Post-Hoc test CS+ > CS- by group (adjusted Tukey HSD)", digits = 3) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
```

## Mobilized effort (AUC) difference (CS+ > CS-) by group
```{r PIT_plot, echo=FALSE, warning=FALSE, cache=TRUE}

# create bin for each mini block
#PIT.clean$trialxcondition    <- as.numeric(PIT.clean$trialxcondition)
#PIT.clean  <- ddply(PIT.clean, "id", transform, bin = as.numeric(cut2(trialxcondition, g = 5)))

PIT.s <- subset (PIT.clean, condition == '1'| condition == '-1')
PIT.s$trialxcondition <- factor(PIT.s$trialxcondition)
PIT.means <- aggregate(PIT.s$AUC, by = list(PIT.s$id, PIT.s$condition, PIT.s$group), FUN='mean') # extract means
colnames(PIT.means) <- c('id','condition', 'group', 'force')

#PIT.trial <- aggregate(PIT.s$AUC, by = list(PIT.s$id, PIT.s$trialxcondition), FUN='mean') # extract means
#colnames(PIT.trial) <- c('id','trialxcondition','force')

### Plot between contrasts

df_est = emmeans(mod, pairwise~ condition|group) # estimate contrasts means by group from the model 
dfP = data.frame(df_est$contrasts); dfP$force = dfP$estimate #create a dataframe
CSp = subset(PIT.means, condition == '1'); CSm = subset(PIT.means, condition == '-1'); cont.means = CSp
cont.means$force = CSp$force - CSm$force; 

dfP$groupi <- ifelse(dfP$group == "1", -0.25, 0.25)
cont.means$groupi <- ifelse(cont.means$group == "1", -0.25, 0.25)
set.seed(666)
cont.means <- cont.means %>% mutate(groupjit = jitter(as.numeric(groupi), 0.25),
                                    grouping = interaction(id, groupi))


pp <- ggplot(cont.means, aes(x = groupi, y = force, 
                             fill = group, color = group)) +
  geom_hline(yintercept=0, linetype="dashed", size=0.4, alpha=0.8) +
  geom_flat_violin(scale = "count", trim = FALSE, alpha = .2, aes(fill = group, color = NA))+
  geom_point(aes(x = groupjit), alpha = .3,) +
  geom_crossbar(data = dfP, aes(y = force, ymin=force-SE, ymax=force+SE), width = 0.2 , alpha = 0.1)+
  #geom_errorbar(data = dfP,aes(group = group, ymin=force-SE, ymax=force+SE),position=position_nudge(x=0.15), size=0.5, width=0.1,  color = "black") + 
  ylab('\u0394 Mobilized effort (CS+ > CS-)')+
  xlab('')+
  scale_fill_manual(values=c("1" = pal[6],"0"=pal[1]), guide = 'none') +
  scale_color_manual(values=c("1" = pal[6],"0"=pal[1]), guide = 'none')  +
  scale_y_continuous(expand = c(0, 0), breaks = c(seq.int(-200,200, by = 50)), limits = c(-200.5,200.5)) +
  scale_x_continuous(labels=c("Obese", "Lean"),breaks = c(-.25,.25), limits = c(-.5,.5)) +
  theme_bw() 

plt = pp + averaged_theme 
pp + html_theme 
```
```{r PIT_saveFIG, echo=FALSE, include = FALSE, warning=FALSE}
cairo_pdf('figures/Figure_PIT_con.pdf')
print(plt)
dev.off()
```

## Mobilized effort (AUC) over time
```{r PIT_time, echo=FALSE, warning=FALSE, cache=TRUE}
# PLOT OVERTIME
labels <- c("0" = "Lean", "1" = "Obese")
PIT.p <- summarySEwithin(PIT.clean,
                         measurevar = "AUC",
                         withinvars = c("trialxcondition","condition"),
                         betweenvars = "group",
                         idvar = "id")

PIT.p$trial <- as.numeric(PIT.p$trialxcondition)
PIT.p = select(PIT.p, c('trial', 'N' , 'AUC', 'sd', 'se', 'ci', 'condition', 'group'))


# plot 
pp <- ggplot(PIT.p, aes(x = as.numeric(trial), y = AUC,
                        color = condition, 
                        fill  = condition))+
  geom_line(alpha = .5, size = 1, show.legend = F) +
  geom_ribbon(aes(ymax = AUC + se, ymin = AUC - se),  alpha=0.4) + 
  geom_point() +
  ylab('Mobilized effort (a.u.)')+
  xlab('Trial')+
  scale_color_manual(labels = c('-1'= 'CS-', "1" = 'CS+'), name="", 
                     values = c("1"= pal[2], '-1'= pal[1])) +
  scale_fill_manual(labels = c('-1'= 'CS-', "1" = 'CS+'), name="", 
                    values = c("1"= pal[2], '-1'= pal[1])) +
  scale_y_continuous(expand = c(0, 0),  limits = c(50,200),  breaks=c(seq.int(50,200, by = 50))) +
  scale_x_continuous(expand = c(0, 0),  limits = c(0,15),  breaks=c(seq.int(1,15, by = 2))) +
  theme_bw() +
  facet_wrap(~group, labeller=labeller(group = labels))


pp + html_theme + theme(strip.background = element_rect(fill="white"), legend.key.size = unit(0.3, "cm"), axis.text.x = element_text(size = 16))
plt = pp + averaged_theme + theme(strip.background = element_rect(fill="white"), legend.key.size = unit(0.8, "cm"), axis.text.x = element_text(size = 16))
```
```{r PIT_time_saveFIG, echo=FALSE, include = FALSE, warning=FALSE}
cairo_pdf('figures/Figure_PIT_time.pdf')
print(plt)
dev.off()
```
# Hedonic Reactivity Test (Analysis)
Formula = Pleasantness ratings ~ condition*group + age + gender+ thirsty + hungry + intensity + Error(id/condition)\
Pleasantness ratings = how pleasant is the liquid solution rated (0-100, with repetitions)   &   condition = Milshake or Tasteless   &   intensity = difference on how intense the liquid solution were rated (mean(Milshake) - mean(Tasteless))
```{r HED, echo=FALSE, include=FALSE, cache=TRUE}
# -------------------------------------- STATS -----------------------------------------------

### Linear Mixed Models 
# Mixed is just a wrapper for lmer to get p-values from parametric bootstrapping #but set to method "LRT" and remove "args_test" to quick check ##
#model = mixed(formula, data = HED, method = "LRT", control = control, REML = FALSE); 
#model = mixed(formula, data = HED, method = "PB", control = control, REML = FALSE, args_test = list(nsim = 10000, cl=cl)) 
model = aov_car(perceived_liking ~ condition*group + age + gender+ thirsty + hungry + intensity + Error(id/condition), data= HED.means, factorize = F, anova_table = list(correction = "GG", es = "none"))
table = nice(model); 

#calculate Partial eta-squared and its 90 % CI for each effect
pes_CI = pes_ci(perceived_liking ~ condition*group + age + gender+ thirsty + hungry + intensity + Error(id/condition), HED.means); 
table$`PES` = pes_CI[,1]
table$`Lower CI` = pes_CI[,2]
table$`Upper CI` = pes_CI[,3]

#calculate exclusion BF01 for each effect
test = extractBF(generalTestBF(perceived_liking ~ condition*group + condition*age + condition*gender + condition*thirsty + condition*hungry + condition*intensity + id, data= HED.means, whichRandom = 'id', neverExclude =  'id', whichModels ="top")); BF = 1/test[1] #switch to BF10 inclusion)); BF = 1/test[1] #switch to BF10 inclusion
table$BF10 = round(BF$bf[order(c(13, 12, 11, 10,  9,  8, 6,  5,  4,  3,  2, 1, 7))],2) # reorder
table$BF10[7] = formatC(BF$bf[13], format = "e", digits = 2)

mod <- lmer(perceived_liking ~ condition*group + age + gender+ thirsty + hungry  +  familiarity + intensity + (condition |id), data = HED, control = control, REML = T) # recompute model with REML = T now for further analysis
ref_grid(mod)  #triple check everything is centered at 0

tab_model(mod, show.p = F,show.intercept = F, show.se = T,  title ="", show.re.var = F, digits = 3, dv.labels = "Pleasantness Ratings", file = "tmp/temp5.html")
```
\
```{r HED_mod, echo=FALSE, warning=FALSE}
tables <- list.clean(readHTMLTable("tmp/temp5.html"), fun = is.null, recursive = FALSE)
tables2 = tables[[1]] %>% janitor::row_to_names(row_number = 1)
tables2 <- as.matrix(tables2) %>% as_tibble()
tables2[is.na(tables2)] <- ""
tables2[1:11,1:4] %>% kbl(caption ="Pleasantness ratings (taste)" ) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F)  %>%  row_spec(0,bold=T,align='c')

tmp =tables2[12:16,1:2]
names(tmp) <- NULL
tmp %>% kbl() %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F)  
```

```{r HED_res}
table %>% kbl( digits = 2) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0,bold=T,align='c')
```

## Pleasantness Ratings (Taste) by condition
```{r HED_plot, echo=FALSE, warning=FALSE, cache=TRUE}

# AVERAGED EFFECT
dfH <- summarySEwithin(HED.means,
                       measurevar = "perceived_liking",
                       withinvars = "condition", 
                       idvar = "id")

dfH$cond <- ifelse(dfH$condition == "1", -0.25, 0.25)
HED.means$cond <- ifelse(HED.means$condition == "1", -0.25, 0.25)
set.seed(666)
HED.means <- HED.means %>% mutate(condjit = jitter(as.numeric(cond), 0.3),
                                  grouping = interaction(id, cond))


pp <- ggplot(HED.means, aes(x = cond, y = perceived_liking, 
                            fill = condition, color = condition)) +
  geom_point(data = dfH, alpha = 0.5) +
  geom_line(aes(x = condjit, group = id, y = perceived_liking), alpha = .3, size = 0.5, color = 'gray') +
  geom_flat_violin(scale = "count", trim = FALSE, alpha = .2, aes(fill = condition, color = NA))+
  geom_point(aes(x = condjit, shape = group), alpha = .3,) +
  geom_crossbar(data = dfH, aes(y = perceived_liking, ymin=perceived_liking-se, ymax=perceived_liking+se), width = 0.2 , alpha = 0.1)+
  ylab('Perceived liking') +
  xlab('Taste') +
  scale_y_continuous(expand = c(0, 0), breaks = c(seq.int(0,100, by = 20)), limits = c(-0.5,100.5)) +
  scale_x_continuous(labels=c("Pleasant", "Neutral"),breaks = c(-.25,.25), limits = c(-.5,.5)) +
  scale_fill_manual(values=c("1"= pal[3], "-1"=pal[1]), guide = 'none') +
  scale_color_manual(values=c("1"=pal[3], "-1"=pal[1]), guide = 'none') +
  scale_shape_manual(name="Group", labels=c("Lean", "Obese"), values = c(1, 2)) +
  theme_bw()

plt <- pp + averaged_theme
pp + html_theme
```
```{r HED_saveFIG, echo=FALSE, include = FALSE, warning=FALSE}
cairo_pdf('figures/Figure_HED.pdf')
print(plt)
dev.off()
```
## Pleasantness Ratings over time
```{r HED_time, echo=FALSE, warning=FALSE, cache=TRUE}

# OVERTIME
HED.t <- summarySEwithin(HED,
                         measurevar = "perceived_liking",
                         withinvars = c("trialxcondition","condition"),
                         idvar = "id")

HED.tg <- summarySEwithin(HED,
                          measurevar = "perceived_liking",
                          withinvars = c("trialxcondition","condition"),
                          betweenvars = 'group',
                          idvar = "id")


# plot 
pp <- ggplot(HED.t, aes(x = as.numeric(trialxcondition), y = perceived_liking,
                        color =condition, fill = condition)) +
  geom_point(data = HED.tg, aes(shape=group), alpha = 0.5) +
  geom_point(data = HED.t) +
  geom_line(alpha = .7, size = 1) +
  geom_ribbon(aes(ymax = perceived_liking + se, ymin = perceived_liking - se),  alpha=0.4) + 
  ylab('Perceived liking')+
  xlab('Trial') +
  scale_shape_manual(name="Group", labels=c("Lean", "Obese"), values = c(1, 2)) +
  scale_color_manual(labels = c('Pleasant', 'Neutral'), name = "",
                     values = c( "1" =pal[3], '-1' =pal[1])) +
  scale_fill_manual(labels = c('Pleasant', 'Neutral'), name = "",
                    values = c( "1" =pal[3], '-1'=pal[1])) +
  scale_y_continuous(expand = c(0, 0),  limits = c(40,100),  breaks=c(seq.int(50,100, by = 10))) +
  scale_x_continuous(expand = c(0, 0),  limits = c(-0.09,20.09),  breaks=c(seq.int(0,20, by = 2))) +
  guides(color=guide_legend(override.aes=list(fill=c(pal[3], pal[1]))))+
  theme_bw()


plt <- pp + averaged_theme + guides(shape = guide_legend(order = 1)) + theme(legend.margin=margin(0,0,0,0), legend.box = "horizontal", legend.key.size = unit(0.4, "cm"), axis.text.x = element_text(size = 16), legend.position = c(0.8, 0.915)) 
pp + html_theme + guides(shape = guide_legend(order = 1)) + theme(legend.margin=margin(0,0,0,0), legend.box = "horizontal", legend.key.size = unit(0.4, "cm"), axis.text.x = element_text(size = 16), legend.position = c(0.8, 0.915)) 

```
```{r HED_time_saveFIG, echo=FALSE, include = FALSE, warning=FALSE}
cairo_pdf('figures/Figure_HED_time.pdf')
print(plt)
dev.off()
```



